---
title: "Cancer Care Expenditures"
author: "Logan Hashmi, Victor Cruz, Charles Lybrand"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---

#Data.world Project

This project explores how much money is spent on cancer care. The data ranges from 2010 to predictions made out to 2020, and includes a breakdown of the types of costs, locations of cancer, and several other filters.

The data and several insights can be found on [data.world](https://data.world/brookslybrand/s18-edv-project-2).

The GitHub Classroom Repository containing all the code for this project can be found [here](https://github.com/CannataUTDV/s18dvproject1-hashmi-cruzdiaz-lybrand.git).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

#Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```

#Insights

Each of the team members began explore the data using [Tableau Public](https://public.tableau.com/en-us/s/). A lot was discovered about the data and about the cost of cancer treatment right now and in the future. Here are a few of these insights (more can be found [here](https://data.world/brookslybrand/s18-edv-project-2/insights))

(Here is where we included Tableau plugins like seen in last class that show some of our insights)

#Main Dataframes
```{r}
source("DataA.R", local = TRUE)
```

#Retrieve Regions from the SuperStore dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/brookslybrand/s18-edv-project-2-dataset"
data.world::set_config(cfg_env("DW_API")) 
cancers <- data.world::query(data.world::qry_sql(
 "   
	select distinct cancer_site
	from cancer_data 
 "), 
dataset = project)
```

#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Cancers <- eventReactive(c(input$selectCancer_1), { 
  library('stringr')
  str_c(input$selectCancer_1, collapse=', ')
})
```

#Create Panel with Select List
The following code creates an input panel for the Interactive Document, which has a [select box](https://shiny.rstudio.com/reference/shiny/latest/selectInput.html) for selecting regions (notice - choices is set to the regions variable that was loaded by the previous query) For a complete list of Shiny functions, please see this [link](https://shiny.rstudio.com/reference/shiny/latest/).

```{r}
inputPanel(
  selectInput("selectCancer_1", label = "Select Cancer Site",choices = cancers, multiple=TRUE),
  sliderInput("selectYear_1", label = "Year:", min = 2010, max = 2020, value = c(2010, 2020), step = 1)
)
```

#Render and Display the Shipping Costs Histograms

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Total Cost Histogram", tabName = "histogram", icon = icon("dashboard"))
      
      
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Total Costs Histogram" tab content
      tabItem(tabName = "histogram",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("Histogram1UI.R",local = TRUE)$value
      )
    )
  )
)
source("Histogram1Server.R", local = TRUE)

```


#Main Discoveries

The thing we found most interesting and important in our dataset was....

(This is where we included the main dashboard and all relevant information)


#Appendix
Data cleaning Code.


